### 2021-04-08 papers/SYRCoSE/regmachine-eventstruct.tex
Regmachine: a bit more 'the'

Program order tracks precedence of events within a single thread. 
Reads-from relation captures the flow of values from 
write events to read events, and ensures that values 
do not appear out of thin-air~\cite{Boehm-Demsky:MSPC14, Lahav-al:PLDI17}.

>>>>

The program order relation tracks precedence of events within a single thread. 
The reads-from relation captures the flow of values from 
write events to read events, and ensures that values 
do not appear out of thin-air~\cite{Boehm-Demsky:MSPC14, Lahav-al:PLDI17}.
